\documentclass[11pt,a4paper, roman]{moderncv}
\usepackage{verbatim}
%% ModernCV themes

\moderncvcolor{black}
\moderncvstyle{banking}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}
\usepackage[square,sort,comma]{natbib}
%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.75]{geometry}

%hyperref
\usepackage[hyperfootnotes=false]{hyperref}
\hypersetup{colorlinks=true, linkcolor=magenta, filecolor=cyan, urlcolor=blue}

\newcounter{bibcount}
%% Personal data
\firstname{Cyril}
\familyname{Creque-Sarbinowski}
\address{220 West 98th Street, Apartment 6K}{New York, NY 10025} 
\mobile{+1~(216)~282~4561} 
\email{ccreque@flatironinstitute.org} 

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Education}
\cventry{2017-2022}{Ph.D in Physics \& Astronomy}{Johns Hopkins University (JHU)}{Baltimore, MD}{}{Advisor: Marc Kamionkowski}  % arguments 3 to 6 can be left empty
\cventry{2013-2017}{B.S. in Physics and Mathematics}{Massachusetts Institute of Technology (MIT)}{Cambridge, MA}{}{}  % arguments 3 to 6 can be left empty
%% ...
\section{Positions Held}
\cventry{Aug. 2022-Present}{Flatiron Research Fellow}{Center for Computational Astrophysics (CCA)}{New York, NY}{}{}
\cventry{Sep. 2022-Present}{Visiting Scholar}{New York University (NYU)}{New York, NY}{}{}
\section{Teaching}
\cventry{Spring 2022}{Virtual Guest Lecturer, \href{https://cyril-creque.github.io/files/teaching/Moravian_PHYS111_Mechanics_SHO.pdf}{Slides}}{PHYS 111: Introductory Physics}{Moravian University}{}{}
\cventry{Spring 2022}{Guest Lecturer, \href{https://cyril-creque.github.io/files/teaching/Brown_PHYS2300_QFTI_Neutrinos.pdf}{Lecture Notes}}{PHYS2300: Quantum Theory of Fields I}{Brown University}{}{}
\cventry{Fall 2017}{Teaching Assistant}{AS.171.107 General Physics for Physical Science Majors}{JHU}{}{Lecturer: Prof. Robert Leheny \& Prof. Rosemary Wyse}
\cventry{Fall 2017}{Section Head}{AS.173.111 General Physics Laboratory I}{JHU}{}{}
%% ...
\section{Awards, Scholarships, Fellowships}
\cventry{2019-2022}{Graduate Research Fellow}{National Science Foundation}{}{}{}
\cventry{2013-2022}{Scholar}{Gates Millenium Scholars Program}{}{}{}
\cventry{2017-2019}{Fellow}{Kelly Miller Fellowship}{}{}{}
%% ...
%% A publications list
\section{Conferences, Workshops, Seminars}
* = \textit{Invited}, Hyperlinks to PDF of slides on topic\\
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/4PT_dCS.pdf}{Seminar*}}{Joint Tufts/MIT Cosmology Seminar}{Feb. 2023}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/4PT_dCS.pdf}{Seminar*}}{Brown University IDEA Seminar}{Feb. 2023}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/dCS_UV_Completions.pdf}{Conference}}{National Society of Black Physicists Annual Conference}{Nov. 2022}
\cvitemwithcomment{Workshop*}{Guest Expert, Cosmology Talks Parity-Violation Mini-Workshop}{Nov. 2022}
\cvitemwithcomment{Seminar*}{Imperial College London}{Nov. 2022}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/dCS_UV_Completions.pdf}{Talk*}}{Ohio State University Astroparticle Lunch Talk}{Sept. 2022}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/dCS_UV_Completions.pdf}{Talk}}{Princeton Universty/Institute of Advanced Study Lunch Series}{Sept. 2022}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/dCS_UV_Completions.pdf}{Workshop (Organizer)}}{NeXus Workshop}{Aug. 2022}
%\cvitemwithcomment{}{Talk Title: Chern-Simons Gravity and Neutrino Self-Interactions}{}
\cvitemwithcomment{Workshop}{Aspen Center for Physics}{May-June 2022}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/Electromagnetic_Charge.pdf}{Seminar*}}{Brown University}{March 2022}
%\cvitemwithcomment{}{Signatures of Electromagnetic Charge in the Universe}{}
\cvitemwithcomment{Workshop}{NeXus Workshop}{June 2021}
%\cvitemwithcomment{}{Talk Title: High Energy Astrophysical Neutrinos (HEAN)}{}
\cvitemwithcomment{Conference}{Pheno 2021}{May 2021}
\cvitemwithcomment{Conference}{XIX International Workshop on Neutrino Telescopes
}{Feb. 2021}
\cvitemwithcomment{Conference}{Neutrino\ 2020}{Jun. 2020}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/EDGES_DM_2019.pdf}{Seminar*}}{Bowdoin College}{Nov. 2019}
%\cvitemwithcomment{}{Talk Title: Direct Millicharge Dark Matter Cannot Explain the Anomalous EDGES Signal}{}
\cvitemwithcomment{Conference}{National Society of Black Physicists Annual Conference}{Nov. 2019}
\cvitemwithcomment{Conference}{Cosmic Controversies, Kavli Institute  for Cosmological Physics}{Oct. 2019}
\cvitemwithcomment{Workshop}{Novel Ideas for Dark Matter, Princeton Center for Theoretical Science}{Jan. 2019}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/IDM_IM_2018.pdf}{Conference}}{National Society of Black Physicists Annual Conference}{Nov. 2018}
%\cvitemwithcomment{}{Talk Title: Searching for Decaying and Annihilating Dark Matter with Line Intensity Mapping}{}
\cvitemwithcomment{\href{https://cyril-creque.github.io/files/talks/IDM_IM_2018.pdf}{Conference}}{Identification of Dark Matter, Brown University}{Jul. 2018}
%\cvitemwithcomment{}{Talk Title: Searching for Decaying Particles with Line Intensity Mapping}{}
\cvitemwithcomment{Workshop}{Second Annual Line-Intensity Mapping Workshop (IM@Hopkins),}{Jul. 2017}
\cvitemwithcomment{}{\phantom{Conference:}Johns Hopkins University}{}
\cvitemwithcomment{Conference}{Neutrinos and Light Particles in Cosmology, }{Jun. 2016}
\cvitemwithcomment{}{\phantom{Conference:\ \ }Berkeley Center for Cosmological Physics}{}
\cvitemwithcomment{Conference}{National Society of Black Physicists Annual Conference}{Feb. 2015}

\nocite{*}
\bibliography{inspire}
\bibliographystyle{hunsrt}



\end{document}
